Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-29 draft/paper1_rachel.tex
Edit sample selection 3

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_diff_new}
      \caption{              
          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for massive
      	  galaxies (grey dots).
      	  The running-median of the mass difference is shown by large red hexagons. On average, \mcmodel{} underestimates the total stellar mass of massive 
          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
          Vertical histograms indicate the mass difference for all galaxies (shaded 
          histogram) and for the ones with \logmtot{}$>11.6$ (empty histogram).
          \textbf{Right:} Difference between \mmax{} and \mtot{} in the same format. 
          The average difference is small (0.02 dex) and with no clear mass--dependence. \rachel{It might be worth explicitly noting the different vertical axis scales in the caption.  I did not notice at first, and if you do not notice then you might draw the wrong conclusion.}}
      \label{fig:mass_diff}
  \end{figure*}

@@

    We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
    algorithm (Jedrzejewski 1987) to estimate the total luminosities of massive 
    galaxies and to measure their one-dimensional stellar mass surface 
    density profiles (\mden{}). 
    This 1-D method is less affected by the issues mentioned above. 
    Also, we will only study galaxies in the radial range where we are less 
    sensitive to either the PSF ($r<5-6$ kpc) or the background subtraction 
    ($r>100$ kpc).
    The region 
    It is worth noting that the PSF

    We prepare large $i$-band postage-stamps for each galaxy that extend to 750 kpc in 
    radius, along with a bad pixel mask and the PSF model. 
    These postage-stamps include all of the light of the galaxy and are large enough to 
    also evaluate the background level. We choose to use $i$-band images because they trace the stellar distributions of 
    massive galaxies at $0.3 \leq z \leq 0.5$ reasonably well 
    (the observed $i$-band corresponds to a rest-frame $g$ or $r$ band), but also 
    because they have better seeing and much lower background levels than the $z$ 
    and $y$ band images (although these in principle may be better tracers of 
    \mden{}).

>>>>

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_diff_new}
      \caption{              
          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for massive
      	  galaxies (grey dots).
      	  The running-median of the mass difference is shown by large red hexagons. 
      	  On average, \mcmodel{} underestimates the total stellar mass of massive 
          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
          Vertical histograms indicate the mass difference for all galaxies (shaded 
          histogram) and for the ones with \logmtot{}$>11.6$ (empty histogram).
          \textbf{Right:} Difference between \mmax{} and \mtot{} in the same format. 
          The average difference is small (0.02 dex) and with no clear mass--dependence. 
          \textbf{Please note that the scales of the vertical axes are different 
            for these two figures.}
          }
      \label{fig:mass_diff}
  \end{figure*}

@@

    We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
    algorithm (Jedrzejewski 1987) to estimate the total luminosities of massive 
    galaxies and to measure their one-dimensional stellar mass surface 
    density profiles (\mden{}). 
    This 1-D method is less affected by the issues mentioned above. 
    Also, we will only study galaxies in the radial range where we are less 
    sensitive to either the PSF or the background subtraction.
    We ignore the inner 6.11 kpc, which is twice the size of 1\asec{} seeing at 
    $z=0.5$.
    Using this conservative choice, we can safely ignore the smearing effect of 
    seeing outside this radius.
    As we will show later, we confirm this by comparing our HSC profiles with 
    observations with higher spatial resolution. 
    As for the impact from background subtraction, we will focus on the profiles 
    within 100 kpc.

    We prepare large $i$-band postage-stamps for each galaxy that extend to 750 kpc 
    in radius, along with a bad pixel mask and the PSF model. 
    These postage-stamps include all of the light of the galaxy and are large enough 
    to also evaluate the background level. We choose to use $i$-band images because 
    they trace the stellar mass distributions of massive galaxies at 
    $0.3 \leq z \leq 0.5$ reasonably well 
    (the observed $i$-band corresponds to a rest-frame $g$ or $r$ band), but also 
    because they have better seeing and much lower background levels than the $z$ 
    and $y$ band images (although these in principle may be better tracers of 
    \mden{}).
